---
title: "rMiW: An installation of the related packages"
author: 
- name: Satoshi Kume
  email: satoshi.kume.1984@gmail.com
- name: Kozo Nishida
date: "`r Sys.Date()`"
graphics: no
package: knitr, magick
output:
    BiocStyle::html_document:
        toc_float: true
vignette: >
    %\VignetteIndexEntry{rMiW}
    %\VignetteEncoding{UTF-8}
    %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r style, echo = FALSE, results = 'asis', message=FALSE}
BiocStyle::markdown()
```

**Last modified:** `r file.info("rMiW_installation.Rmd")$mtime`<br />
**Compiled**: `r date()`

# Getting started

`r Rpackage("rMiW")` is a R package distributed in kumeS's GitHub site.

To install the package, start R and enter:

```{r echo=TRUE, eval=FALSE}
#Check for the installation (30 June 2021)
install.packages( "devtools" )
devtools::install_github( "kumeS/rMiW" )
library( "rMiW" )

#if you want to remove the package
#remove.packages("rMiW", lib=.libPaths())

```

In addition, you want to install an ExperimentHub package 
`r Rpackage("BioImageDbs")` from Bioconductor.

```{r echo=TRUE, eval=FALSE}
#Check for the installation (30 June 2021)
install.packages("BiocManager")
BiocManager::install("ExperimentHub", force = TRUE)
BiocManager::install("BioImageDbs", force = TRUE)

#Load
library(ExperimentHub)
library(BioImageDbs)

```

# Optional setting at OECU

Run the following commands in the R console.

```{r echo=TRUE, eval=FALSE}
#Proxy setting at OECU
if(T){
proxy_url = "http://wwwproxy.osakac.ac.jp:8080"
Sys.setenv("http_proxy" = proxy_url)
Sys.setenv("https_proxy" = proxy_url)
Sys.setenv("ftp_proxy" = proxy_url)
}

```

# Session information {.unnumbered}
```{r sessionInfo, echo=FALSE}
sessionInfo()
```

